First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-07-04 eg6-letters/coherent/dvcs_he4_prl.tex
Add reference to the technical RTPC paper

In the kinematic range of the present experiment, the recoil $^4$He nuclei 
have low momentum, averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC). The 
RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC was the target cell, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
gaseous $^4$He at 6~atm. The experiment (E08-024)~\cite{Hafidi:2008pr} collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei using elastic scattering 
($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.

@@

>>>>

In the kinematic range of the present experiment, the recoil $^4$He nuclei 
have low momentum, averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light radial time projection chamber (RTPC). The 
RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
solenoid magnet. In the center of the RTPC was the target cell, a $25$-cm-long 
and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
gaseous $^4$He at 6~atm (see~\cite{Dupre:2017upj} for a detailed description of 
the RTPC and its performances). The experiment (E08-024)~\cite{Hafidi:2008pr} collected
data over 40 days at the end of 2009 using a 
nearly 100\% duty factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
for the detection of $^4$He nuclei using elastic scattering 
($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.

@@

\bibitem{Dupre:2017upj} 
  R.~Dupré {\it et al.},
  arXiv:1706.10160 [physics.ins-det].
  (submitted to Nucl.\ Instrum.\ Meth.\ A)
